---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/factcheck.svg?branch=master)](https://travis-ci.org/news-r/factcheck)
<!-- badges: end -->

# factcheck

Fact check publishers or queries, create claims and more.

## Installation

``` r
# install.packages("remotes")
remotes::install_github("news-r/factcheck")
```

## Setup

Get a free key from the [Google Cloud Platform](https://console.cloud.google.com) (formerly Google Console).

```r
factcheck_key("xxXXxxXx")
```

Note that you can specify the `FACTCHECK_API_KEY` key as an environment variable in your `.Renviron` for convenience.

## ROADMAP

- [x] Fact Check
- [x] Authentication
- [ ] Create claims
- [ ] Get created claims
- [ ] Delete created claims
- [ ] Edit claims

## Example

```{r example}
library(factcheck)

# Claims on Trump in English that are maximum 10 days old
fact_check("Trump", lang = "en-US", days_old = 10)

# Claims made on the New York Times
fact_check(publisher = "nytimes.com")
```
